Project management is a necessary part of group  project. Trello is a easy tool for us to plan this project well. We set four statements for anything we want to do: 'To Do', 'Started', 'Review' and 'Done'. At the same time, six labels are built with different colours to identify their kinds of tasks: 'Data', 'Documentation', 'Server', 'Android App', 'Text Analysis' and 'Meeting Prep'. All tasks will be discussed at week meeting and assigned to 'To Do' list. When team member who is responsible for the task will drag this task card to 'Started' list to inform others that this task is being done. After this task has been finished, team member will move this task to 'Review' list to tell others to check and evaluate it. In the next meeting, team members will evaluate all tasks in the 'Review' list and decide to move them to 'Done' list. Each card is an action item of choosing which is as simple as an item on a shopping list.\\
Github is designed very well for group developing. A repository called 'Twitter for Traffic' is built in Github.We separate project into several parts. We create a 'classifier' file for data mining and 'data\_acquisition' file to retrieve tweets and TfL data. 'mobile\_client' folder is built for Android application development. 'mock\_server' and 'server' folders are platform providing data for mobile client. A folder called 'scrapbook' is created for each members to store source codes and test each unit function of this project. Each team member track file in project and periodically commit the state of the project when a saved point wanted. Then we can share that history with other developers for collaboration, merge between everyone's work, and compare or revert to previous versions of the project or individual files. What's more, wiki tab can enable team members to add any information that which is useful to project but others don't know.\\